### 2021-02-16 Chapter-1/Chapter-1.tex
update

\section{Address-based Side-channel Attacks}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most of the attack allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

@@

\section{Defense}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

@@

\section{Binary Analysis}
Binary analysis is the process of automatically inferring program behaviors from
the binary executable.
It plays a critical role from a security viewpoint. For many programs, like malware, Commercial off-the-shelf (COTS) application, source code are typically not
available. Besides, some low-level information, including memory accesses and cache
accesses, is only available on the binary code level. As many side-channel vulnerabilities
are typically low-level problem, we believe binary analysis are more suitable than
source code level analysis.

Binary analysis can be categorized into two groups depending when the analysis is
launched.
\begin{itemize}
    \item Static Analysis infer analyzing the binary program without running it. Previous studies focus on addressing several open problems, including identifying
    function entry points~\cite{184521, Wang17a}, resolving indirect jumps, disambiguating code and data and solving alias memory address. Static analysis
    lacks the run-time information, which may lead to false positives and false 
    negatives. However, static analysis typically can have better coverage as it can
    reason about every possible execution paths.
    \item Dynamic Analysis involving analyzing a binary code as it executes. Tools
    that perform dynamic analysis usually need to instrument the binary code.  
    Although dynamic analysis can only reason only one execution path. It is usually more precise than static analysis.
\end{itemize}

In this dissertation, we detected side-channel vulnerabilities by trace-based analysis.
It consists of two steps. The first step, called online trace logging, collect run-time
information for the targeted program under the dynamic binary instrumentation (DBI)
to collect necessary information. The second step, called offline analysis, run
several analysis (e.g., taint analysis, symbolic analysis) on the top of traces.

Existing binary analysis frameworks, like Angr, BAP and Bitblaze combine both static
and dynamic analyses, are applicable to a series of tasks. However, those frameworks
are not suitable for the following reasons. 
\begin{itemize}
    \item Existing binary analysis frameworks transfer the machine code into
    architecture-independent intermediate representatives (IR) and then run the
    analysis. The IR design, which simplify the implementation and support multiple
    architectures, introduces imprecision to the analysis results as well because some
    information like cache accesses, control-flow transfers are lost during the IR
    transformation.
    \item Coverage is one of the concerns when they design the frameworks. 
    As a result, they rely on constraint solvers to find different inputs that can
    trigger different paths. As constraint solving is known for time-consuming. It is
    one of the obstacles to make analyses salable.
    However, we will show for many tasks, like binary similarity comparisons and side-channel vulnerability detection. We can
    reduce the call to the solver just by fuzzing the formula. The design will
    significantly reduce the overhead.
\end{itemize}
To solve the above problem, we propose Phoenix, a trace-oriented binary analysis
framework. Phoenix is a dynamic binary analysis framework that provide several 
functioning including dynamic symbolic execution engine, dynamic taint analysis
engine, AST representation of X86 and binding for STP solvers. It run 
execution on the top X86 instructions and symbolically reason the program behaviours.
Our preliminary results show that Phoenix has a better performance compared to 
many existing works, which makes it scalable to real-world applications.

>>>>

\section{Address-based Side-channel}
\subsection{Attack}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most of the attack allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

@@

\subsection{Defense}

Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt.

On the contrary, software approaches are
usually easy to implement. By removing the above two kinds of code patterns, developers protect their 
code from a seris of side-channel attacks.
Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

@@

### 2021-02-16 Chapter-2/Chapter-2.tex
update

>>>>

\section{Binary Analysis}
Binary analysis is the process of automatically inferring program behaviors from
the binary executable.
It plays a critical role from a security viewpoint. For many programs, like malware, Commercial off-the-shelf (COTS) application, source code are typically not
available. Besides, some low-level information, including memory accesses and cache
accesses, is only available on the binary code level. As many side-channel vulnerabilities
are typically low-level problem, we believe binary analysis are more suitable than
source code level analysis.

Binary analysis can be categorized into two groups depending when the analysis is
launched.
\begin{itemize}
    \item Static Analysis infer analyzing the binary program without running it. Previous studies focus on addressing several open problems, including identifying
    function entry points~\cite{184521, Wang17a}, resolving indirect jumps, disambiguating code and data and solving alias memory address. Static analysis
    lacks the run-time information, which may lead to false positives and false 
    negatives. However, static analysis typically can have better coverage as it can
    reason about every possible execution paths.
    \item Dynamic Analysis involving analyzing a binary code as it executes. Tools
    that perform dynamic analysis usually need to instrument the binary code.  
    Although dynamic analysis can only reason only one execution path. It is usually more precise than static analysis.
\end{itemize}

In this dissertation, we detected side-channel vulnerabilities by trace-based analysis.
It consists of two steps. The first step, called online trace logging, collect run-time
information for the targeted program under the dynamic binary instrumentation (DBI)
to collect necessary information. The second step, called offline analysis, run
several analysis (e.g., taint analysis, symbolic analysis) on the top of traces.

Existing binary analysis frameworks, like Angr, BAP and Bitblaze combine both static
and dynamic analyses, are applicable to a series of tasks. However, those frameworks
are not suitable for the following reasons. 
\begin{itemize}
    \item Existing binary analysis frameworks transfer the machine code into
    architecture-independent intermediate representatives (IR) and then run the
    analysis. The IR design, which simplify the implementation and support multiple
    architectures, introduces imprecision to the analysis results as well because some
    information like cache accesses, control-flow transfers are lost during the IR
    transformation.
    \item Coverage is one of the concerns when they design the frameworks. 
    As a result, they rely on constraint solvers to find different inputs that can
    trigger different paths. As constraint solving is known for time-consuming. It is
    one of the obstacles to make analyses salable.
    However, we will show for many tasks, like binary similarity comparisons and side-channel vulnerability detection. We can
    reduce the call to the solver just by fuzzing the formula. The design will
    significantly reduce the overhead.
\end{itemize}
To solve the above problem, we propose Phoenix, a trace-oriented binary analysis
framework. Phoenix is a dynamic binary analysis framework that provide several 
functioning including dynamic symbolic execution engine, dynamic taint analysis
engine, AST representation of X86 and binding for STP solvers. It run 
execution on the top X86 instructions and symbolically reason the program behaviours.
Our preliminary results show that Phoenix has a better performance compared to 
many existing works, which makes it scalable to real-world applications.
